A Survey on Ordered Binary Decision Diagrams

### 2015-09-14 paper.tex
Add citations

Today, garbage collecion is a well-known topic. It is used to free up unnecessary
allocated or unused memory. To accomplish this, the garbage collection has to know
about which parts of the memory are \textit{dead} and thus can be freed. A node
of an OBDD is called \textit{dead} if the reference count of it is equal to zero.
The reference count of a node $x$ is decremented every time a corresponding
formula is freed. If the reference count of $x$ reaches zero, the reference counts
of $lo(x)$ and $hi(x)$ are decremented recursively.

Instead of freeing dead nodes instantaneously, there exists a \textit{reclaim}
operation which is performed whenever a lookup in the computed-table returns a
dead node $x$. Such a reclaim operation increments the reference count of $x$ and
propagates the reclaim operation to $lo(x)$ and $hi(x)$, respectively.\tbr

>>>>

Today, garbage collecion is a well-known topic. It is used to free up unnecessary
allocated or unused memory. To accomplish this, the garbage collection has to know
about which parts of the memory are \textit{dead} and thus can be freed. A node
of an OBDD is called \textit{dead} if the reference count of it is equal to zero.
The reference count of a node $x$ is decremented every time a corresponding
formula is freed. If the reference count of $x$ reaches zero, the reference counts
of $lo(x)$ and $hi(x)$ are decremented recursively~\cite{BRACE90}.

Instead of freeing dead nodes instantaneously, there exists a \textit{reclaim}
operation which is performed whenever a lookup in the computed-table returns a
dead node $x$. Such a reclaim operation increments the reference count of $x$ and
propagates the reclaim operation to $lo(x)$ and $hi(x)$,
respectively~\cite{BRACE90}. \tbr
